The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-29 article.tex
fixed last figure env

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better,
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~6\ref{fig:sdgstereo}.

@@

\subsection*{Figure 1 - Atom type information specified for a sp3-hybridized
carbon.}\label{fig:atomtype}
\begin{verbatim}
  <at:AtomType rdf:ID="C.sp3">
    <at:categorizedAs rdf:resource="&cdkat;C.tetrahedral"/>
    <at:hasElement rdf:resource="&elem;C"/>
    <at:hybridization rdf:resource="&at;sp3"/>
    <at:formalCharge>0</at:formalCharge>
    <at:lonePairCount>0</at:lonePairCount>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
  </at:AtomType>
\end{verbatim}

>>>>

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better,
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

@@

\begin{figure}[h!]
\caption{\csentence{Atom type information specified for a sp3-hybridized
carbon.}}
\begin{verbatim}
  <at:AtomType rdf:ID="C.sp3">
    <at:categorizedAs rdf:resource="&cdkat;C.tetrahedral"/>
    <at:hasElement rdf:resource="&elem;C"/>
    <at:hybridization rdf:resource="&at;sp3"/>
    <at:formalCharge>0</at:formalCharge>
    <at:lonePairCount>0</at:lonePairCount>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
    <at:formalBondType rdf:resource="&bo;single"/>
  </at:AtomType>
\end{verbatim}
  \label{fig:atomtype}
\end{figure}
